---
title: "R Notebook"
output: html_notebook
---




1. Title: Haberman's Survival Data

   The dataset contains cases from a study that was conducted between
   1958 and 1970 at the University of Chicago's Billings Hospital on
   the survival of patients who had undergone surgery for breast
   cancer.

5. Number of Instances: 306

6. Number of Attributes: 4 (including the class attribute)

7. Attribute Information:
   1. Age of patient at time of operation (numerical)
   2. Patient's year of operation (year - 1900, numerical)
   3. Number of positive axillary nodes detected (numerical)
   4. Survival status (class attribute)
         1 = the patient survived 5 years or longer
         2 = the patient died within 5 year

8. Missing Attribute Values: None


```{r}
setwd('./')
haberman <- read.table('haberman.data',sep=',',col.names = c('age','yearOfOperation', 'nodes', "survivalStatus"))

head(haberman)
```



```{r}

#all data
summary(haberman)

#Survived
summary(haberman[haberman$survivalStatus == 1,])
#Died
summary(haberman[haberman$survivalStatus == 2,])


```




```{r}

#Present all four grapths in the same Layout matirx
hist(haberman$age)
hist(haberman$nodes)
hist(haberman$yearOfOperation)
pie(table(haberman$survivalStatus))

```




```{r}
#no clear linear correlation
pairs(haberman,col=haberman$survivalStatus)

```



```{r}
#Correlation analysis
cor(haberman)
```




```{r}

#PCA analysis

install.packages('FactoMineR', dependencies = TRUE)
library('FactoMineR')
result<-PCA(haberman)
summary(result)
```

